A meta-analysis of mental rotation ability in the first years of life

### 2022-04-11 code/analysis.Rmd
Add Bayesian multilevel model

```{r, setup, include=FALSE}
# Load packages
library(here)
library(ggridges)
library(tidyverse)
library(magrittr)
library(metafor)

# Global chunk options
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

@@

>>>>

```{r, setup, include=FALSE}
# Load packages
library(here)
library(ggridges)
library(tidyverse)
library(magrittr)
library(metafor)
library(brms)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  fig.height = 10,
  fig.width = 7.5,
  out.width = "100%"
)
```

@@

```{r, brms, echo=TRUE}
# Specify priors
priors <- c(
  prior(normal(0, 1), class = "Intercept"),
  prior(exponential(1), class = "sd")
)

# Run Bayesian multilevel model
res_brm <- brm(
  yi | se(sei) ~ 1 + (1 | group / id),
  data = dat_r,
  prior = priors,
  cores = 4,
  chains = 4,
  iter = 2000,
  sample_prior = TRUE,
  save_pars = save_pars(all = TRUE)
)
summary(res_brm)

# Sensitivity analysis
list(
  "ic_uninformative" = c(
    prior(uniform(-3, 3), class = "Intercept"),
    prior(exponential(1), class = "sd")
  ),
  "ic_informative" = c(
    prior(normal(0, 0.2), class = "Intercept"),
    prior(exponential(1), class = "sd")
  ),
  "sigma_uninformative" = c(
    prior(normal(0, 1), class = "Intercept"),
    prior(uniform(0, 5), class = "sd")
  ),
  "sigma_informative" = c(
    prior(normal(0, 1), class = "Intercept"),
    prior(exponential(0.1), class = "sd")
  )
) %>%
  map(function(priors) update(res_brm, prior = priors)) -> res_sens
```
